When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-03-07 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
started exploratory

>>>>

# Exploratory analysis

To investigate the apparent group difference between the SVs of participants with NFC scores below and above the median in higher $n$-back levels, we computed an rmANOVA with the within-factor level and the between-factor NFC group.
There was no main effect of NFC group (`r apa_print(explor_model)$full_result$nfcmedian`, `r apa_print(explor_BF)$table[2,"statistic"]`), but a main effect of the $n$-back level (`r apa_print(explor_model)$full_result$level`, `r apa_print(explor_BF)$table[1,"statistic"]`) and an interaction (`r apa_print(explor_model)$full_result$nfcmedian_level`).
Post-hoc tests showed that
